% Graph-based model transformations have become in the last few years the main
% means for manipulating models in model-driven development. Their simplicity,
% their allowance for mathematical treatment, and the fact that they can natively
% manipulate domain-specific concepts expressed in metamodels, all make
% graph-based model transformations an excellent compromise between strong
% theoretical foundations and applicability to real-world problems.
% Because of the importance of graph-based model transformations both in the
% academic and the industrial arenas, their verification is of prime importance.
Model transformations are at the center of model-driven development, making
pragmatic and usable tools for their verification indispensable. In this paper
we introduce SyVOLT (Symbolic Verifier of mOdeL Transformations)~\cite{syvolt},
an Eclipse plugin that allows verifying pre / post-condition structural
contracts on model transformations. SyVOLT's operation relies on a theoretical framework
that has been developed for the DSLTrans model transformation language. In this
framework, pre / post-condition contracts can be shown to either hold for all
input/output pairs resulting from executing a given DSLTrans model
transformation, or not to hold for at least one of those input/output
pairs~\cite{Lucio2014}.

% A fully
% automatic property prover based on this theory has been shown to be applicable
% to industrial problems~\cite{Selim2014}.

Extensive work exists on the verification of different aspects of model
transformations~\cite{AmraniLSCDVTC12}. In~\cite{Vallecillo2012} the
authors describe a method where `Tracts' can be specified for model
transformations. Tracts resemble SyVOLT's contracts and define a set
of constraints on the source and target metamodels, a set of source-target constraints, and a tract test suite, i.e., a collection of source models
satisfying the source constraints. The accompanying TractsTool can then
automatically test the transformation by verifying if all source/target model
pairs satisfy the constraints in the tract test suite.
Several other approaches support the testing of model transformations based
on different kinds of contracts such as model fragments~\cite{Mottu2008}, graph
patterns~\cite{Guerra12,BaloghBCGHMPPRVa10}, Triple Graph Grammars (TGGs)~\cite{WieberAS14} or dedicated testing
languages~\cite{Garcia-Dominguez11}. 

The tool described in \cite{Buettner2013} automatically transforms
transformations in a number of transformation languages (such as ATL) to OCL. Verification is then
done using a model finder which will attempt to find a counter-example to the
property being proved. Anastasakis et al.~\cite{Anastasakis07}
translate model transformations to Alloy in order to verify if given
assertions hold for the given transformations. Both these
approaches attempt to exhaustively verify the model transformation, as SyVOLT
does. However, while SyVOLT guarantees that all counter-examples to a contract
are always found, this is not granted by the two approaches introduced above.

The distinguishing feature of SyVOLT is that, unlike the methods described
above, our tool allows for contracts to be proved for all possible
transformation executions, i.e., for all possible input models.
However, we share with most tools described above the same implication idea: the
pre-condition of a contract sets constraints on the input models to the
transformation, and the post-condition defines constraints on the output model.





